### 2016-07-03 case-studies.tex
Edits.

Next, we focus our attention on a Twitter-like microblogging site that
is one the sample applications shipped with a popular textbook on
Ruby-on-Rails~\cite{railsbook}. One of the invariants that the
application chooses to enforce is the referential integrity between
microposts and authors. The application enforces this invariant
entirely in the user space by relying on database-backed transactions
(this behaviour is typical of Rails applications~\cite{bailisferal}).
For instance, deletion of a user is carried out in a transaction that
also includes the deletion of microposts authored by the user.
However, concurrent observers can nonetheless witness violations of
referential integrity. To measure the likelihood of such anomalies in
practice, we first populated a Postgres database with 1000 user
accounts, each user with 50 microposts and 20 followers, choosen
uniformly at random. We then constructed experiments with 64
concurrent clients performing deletions and timeline reads of randomly
choosen users in 1:7 ratio, and witnessed a maximum of 250 violations
of referential integrity. We then instantiated our framework for an
{\sc sc} store with various ANSI SQL isolation levels for user
deletions and timeline reads, and obtained a proof that {\sc rc} is
sufficient for deletions, whereas reads require {\sc rr}. The proof is
applicable for MySQL, which implements ANSI isolation.  Since
Postgres's isolation levels are stronger than corresponding ANSI
levels, using \rulelabel{RG-Conseq} rule (Fig.~\ref{fig:rg-rules}), we
also obtain a correctness proof for Postgres.

>>>>

Next, we focus our attention on a Twitter-like microblogging site that
is one the sample applications shipped with a popular textbook on
Ruby-on-Rails~\cite{railsbook}. One of the invariants that the
application chooses to enforce is the referential integrity between
microposts and authors. The application enforces this invariant
entirely in the user space by relying on database-backed transactions
(this behaviour is typical of Rails applications~\cite{bailisferal}).
For instance, deletion of a user is carried out in a transaction that
also includes the deletion of microposts authored by the user.
However, concurrent observers can nonetheless witness violations of
referential integrity. To measure the likelihood of such anomalies in
practice, we first populated a Postgres database with 1000 user
accounts, each user with 50 microposts and 20 followers, choosen
uniformly at random. We then constructed experiments with 64
concurrent clients performing deletions and timeline reads of randomly
choosen users in 1:7 ratio, and witnessed a maximum of 250 violations
of referential integrity. We then instantiated our framework for an
{\sc sc} store with various ANSI SQL isolation levels for user
deletions and timeline reads, and obtained a proof that {\sc rc} is
sufficient for deletions, whereas reads require {\sc rr}. The proof is
immediately applicable for MySQL, which implements ANSI SQL isolation
levels. Since Postgres's isolation levels are stronger than the
corresponding ANSI levels, \rulelabel{RG-Conseq} rule
(Fig.~\ref{fig:rg-rules}) lets us deduce that the same choice of
isolation levels also work on Postgres. Indeed, experiments confirmed
this judgment.
